Demo for IEEE Journals

### 2020-02-19 Paper.tex
Another Update
Co-authored-by: 465003502@qq.com <465003502@qq.com>

Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Here is an equation:

@@

>>>>

\subsubsection{Location System}
\subsubsection{Sensors}

content

\begin{table}[h]
    % \Large
    \caption{Sample Table}
    \begin{center}
        \begin{tabular}{|p{1cm}|p{2cm}|p{1cm}|p{2cm}|}
            \hline
            Sensors & Energy Consumption & Accuracy & Description \\ \hline
            Blood Pressure & 50mW & ~2\% & This Description should be displays in multiple lines if it is this long. \\ 
            \hline
        \end{tabular}
    \end{center}
\end{table}

@@

Paragraph three
